---
title: "Main Script"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
`output: html_document` gives the following knittr error and does not produce a html file  
```
|     Backtrace:  
|      1. rmarkdown::render("utils.Rmd")  
|      2. knitr::knit(knit_input, knit_output, envir = envir, quiet = quiet)  
|      3. knitr:::process_file(text, output)  
|      4. knitr:::split_file(lines = text)   
|      5. base::lapply(...)  
|      6. knitr (local) FUN(X[[i]], ...)  
|      7. knitr:::parse_block(g[-1], g[1], params.src, markdown_mode)  
|     
|     Quitting from lines 15-33 [unnamed-chunk-1] (main.Rmd)  
|     Execution halted  
```
1. I adhere to [Google's R Style Guide](https://google.github.io/styleguide/Rguide.html)  
2. Before installing additional packages, make sure to install [Rtools](https://cran.r-project.org/bin/windows/) although you are not building R or R package  
3. Check packages loaded and more on `sessionInfo()` or `getRversion()`  
```{r, include = FALSE }
# The magrittr package is included in the core tidyverse, so you can use %>% whenever you load the tidyverse
library(tidyverse)

rmarkdown::render("tdi03.Rmd")
rmarkdown::render("utils.Rmd")
rmarkdown::render("bc.Rmd")
rmarkdown::render("bc_cities.Rmd")
```

The first chunk (invisible and separate from this) includes the following lines of code:  
```
|     {r, include = FALSE }  
|     The magrittr package is included in the core tidyverse, so you can use %>% whenever you load the tidyverse  
|     library(tidyverse)  
|        
|     rmarkdown::render("tdi03.Rmd")  
|     rmarkdown::render("utils.Rmd")  
|     rmarkdown::render("bc.Rmd")  
|     rmarkdown::render("bc_cities.Rmd")  
```

`include = FALSE` argument can be used to suppress ALL outputs like below, including plots  
```
|     |......                                              |     12% [unnamed-chunk-1]  
|     processing file: bc.Rmd  
|     output file: bc.knit.md  
|     "C:/Program Files/RStudio/resources/app/bin/quarto/bin/tools/pandoc" +RTS -K512m -RTS bc.knit.md --to html4 --from ...  
|     Output created: bc.html  
```  
* The `render` works with .Rmd files whereas `source()` does .R files  
* Directory path defaults to the one calling script i.e. this file!  
```{r}
countColTitle <- "Count"

# df_accounts <- GetCbarData()
df_accounts <- GetTdi03Data()

# Useful data frame info
dim(df_accounts)
# str(df_accounts)  
# summary(account_open_df)
```

```{r}
df_bank_counts <- CountByCategory(df_accounts, "Bank", countColTitle)
df_bank_counts
```

```{r}
ShowCountsByBankInBars(df_bank_counts, countColTitle)
```

```{r}
df_city_counts <- CountByCategory(df_accounts, "City", countColTitle)
head(SortByColName(df_city_counts, countColTitle, TRUE))
```

```{r}
df_city_coords <- GetCityCoords()
head(df_city_coords)
```

```{r}
df_city_coords_with_counts <- AddCountsToCityCoords(df_city_counts, df_city_coords, countColTitle)
head(df_city_coords_with_counts)
```

```{r}
# A list of cities not included in `df_city_coords`
df_city_not_included <- GetCityNameWithNoCoords(df_city_counts, df_city_coords, countColTitle)

SortByColName(df_city_not_included, countColTitle, TRUE)
```

```{r}
objBc <- GetBcRaster()
dim(objBc$rastBc)
```

```{r}
#convert the data frame into shapefile 
vect_cities <- vect(df_city_coords, geom=c("LongDD", "LatDD"))

plot(objBc$polygonBc, main = "BC Map")
```

```{r, out.width = '80%'}
# This line has to be in the SAME chunk to be added to the previous plot!
# `pch = 20`: smooth circle shape
plot(objBc$polygonBc)
plot(vect_cities, pch=20, col="blue", cex = 0.8, alpha = 0.4, main = "All Account Locations", add = TRUE)
```

```{r}
plot(objBc$polygonBc)
# `sqrt()` so that the symbol areas are directly proportional to the quantities
plot(vect_cities, pch=20, col="blue", cex = sqrt(df_city_coords_with_counts[, countColTitle]/3), alpha = 0.4, main = "Major Account Locations", add = TRUE)
```